### 2016-12-13 poster/poster.tex
Updates to poster

\headerbox{Logos \& Graphs}{name=results,column=1,row=0.30, span=1}{
\includegraphics[width=.24\columnwidth]{graphics/TensorFlow.png}
\includegraphics[width=.24\columnwidth]{graphics/theano.jpeg}
\includegraphics[width=.24\columnwidth]{graphics/DyNet.pdf}

% placeholdering for more appropriate graph
Total runtime on various subtasks:

\begin{tabular}{c|ccc}
Time & Dynet & TensorFlow & Theano \\ \hline
Convergence & & 35h 25' & \\
Train epoch & & 6h57' &  \\
Test epoch & & 7'45'' & \\
Train batch & & 5'' &  \\
Test batch & & $<$1'' & \\
\end{tabular}
}

@@

%% Box 3
\headerbox{Development experience}{name=methods,column=1,row=0.65, span=1}{
\setlength{\extrarowheight}{3pt}
\begin{tabularx}{\textwidth}{l|X|X}
\textbf{Framework}  & \textbf{Pros} & \textbf{Cons} \\
\hline
TensorFlow   & Easy to use; good support for RNNs and language models &
    Symbolic computation graph is hard to debug; seems slower than others \\
\hline
Theano  & ``Lower level'' operations $\rightarrow$ highly customizable &
    No built-in support for RNNs (either need to implement or use a wrapper like Keras) \\
\hline
DyNet   & TODO   & TODO \\
\end{tabularx}
}

@@

%% BOX 0
\headerbox{Function calls}{name=results,column=2,row=0, span=1}{
%\begin{itemize}
%\item Time per epoch (for each system)
%\item Time per batch
%\item Most used function/ most resources consumed by (for each system)
%\item Metrics for that function (possibly others that are shared?)
%\item Time to create computation graph
%\end{itemize}

>>>>

\headerbox{Logos \& Graphs}{name=results,column=1,row=0.30, span=1}{
%\includegraphics[width=.3\columnwidth]{graphics/TensorFlow.png}
%\includegraphics[width=.3\columnwidth]{graphics/theano.jpeg}
%\includegraphics[width=.3\columnwidth]{graphics/DyNet.pdf}

Replacement image here?

% placeholdering for more appropriate graph
\begin{center}
Total runtime on various subtasks, using one GPU:
\end{center}

\bgroup
\def\arraystretch{1.1}
\setlength\tabcolsep{5mm}
\begin{tabular}{c|ccc}
Time & Dynet & TensorFlow & Theano \\ \hline
Convergence & 26h10m & 35h25m & (TBD)\\
Train epoch & x & 6h57m & 6h35m \\
Test epoch & x & 7m45s & 24m \\
Train batch & 1s & 5s & x \\
Test batch & < 1s & $<$1s & x \\
\end{tabular}
\egroup

@@

%% Box 3
\headerbox{Development experience}{name=methods,column=1,row=0.65, span=1}{

\setlength{\extrarowheight}{3pt}
\begin{tabularx}{\textwidth}{l|X|X|X}
\textbf{Framework}  & \textbf{Pros} & \textbf{Cons} \\
\hline
TensorFlow   & Easy to use; good support for RNNs and language models &
    Symbolic computation graph is hard to debug; seems slower than others \\
\hline
Theano  & ``Lower level'' operations $\rightarrow$ highly customizable &
    No built-in support for RNNs (either need to implement or use a wrapper like Keras)  \\
\hline
DyNet   & Allows flexible models that change during computation & Less documentation and support; fragile dependencies  \\
\end{tabularx}
}

@@

%% BOX 0
\headerbox{Function-level metrics}{name=results,column=2,row=0, span=1}{
%\begin{itemize}
%\item Time per epoch (for each system)
%\item Time per batch
%\item Most used function/ most resources consumed by (for each system)
%\item Metrics for that function (possibly others that are shared?)
%\item Time to create computation graph
%\end{itemize}
